% DLADE Open Positions - canonical editable XeLaTeX source
% Compile with:
%   xelatex DLADE-open-positions.tex
% Run XeLaTeX a second time if hyperlinks or metadata are changed.
%
% The most frequently edited text is collected immediately below.
\documentclass[10pt]{article}

\usepackage[a4paper,margin=0mm,noheadfoot]{geometry}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage[absolute,overlay]{textpos}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{microtype}

\setmainfont{TeX Gyre Heros}
\newfontfamily\DisplayFont{TeX Gyre Termes}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\TPHorizModule}{1mm}
\setlength{\TPVertModule}{1mm}

% ---------- Editable information ----------
\newcommand{\RecruitmentYear}{2027}
\newcommand{\PhDOpenings}{3}
\newcommand{\PostdocOpenings}{4}
\newcommand{\FundingPeriod}{January 2027 - June 2031}
\newcommand{\PhDStart}{September 2027}
\newcommand{\PostdocStart}{January 2027}
\newcommand{\FirstReviewDate}{August 31, 2026}
\newcommand{\EmailUser}{dalianade}
\newcommand{\EmailDomain}{foxmail.com}
\newcommand{\Website}{https://dalianade.github.io/}
\newcommand{\ObfuscatedEmail}{\EmailUser\textbf{(at)}\ \EmailDomain}

% ---------- Brand palette ----------
\definecolor{DLADEBlue}{HTML}{075EB7}
\definecolor{DLADENavy}{HTML}{063B6F}
\definecolor{DLADENavyDark}{HTML}{022B52}
\definecolor{DLADEYellow}{HTML}{FFCC00}
\definecolor{DLADEInk}{HTML}{183A59}
\definecolor{DLADEMuted}{HTML}{60778D}
\definecolor{DLADEPale}{HTML}{EEF4F9}
\definecolor{DLADEPaleBlue}{HTML}{DDEAF5}
\definecolor{DLADELine}{HTML}{CAD8E5}
\definecolor{DLADEHeaderMuted}{HTML}{C5D7E7}
\definecolor{DLADEWhiteMuted}{HTML}{D6E2ED}

\hypersetup{
  pdftitle={Open PhD and Postdoc Positions in Applied Mathematics - DLADE},
  pdfauthor={DaLian Analysis and Differential Equations},
  pdfsubject={PhD and postdoctoral recruitment at Dalian University of Technology},
  colorlinks=true,
  urlcolor=DLADEYellow
}

% ---------- Reusable visual components ----------
\newcommand{\DLADELogo}{%
  \begin{tikzpicture}[baseline=-1.2mm,x=1mm,y=1mm]
    \draw[white,line width=.45mm] (6,6) circle (6);
    \draw[white,line width=.35mm,line cap=round] (2.7,2.7)--(9,9.2);
    \draw[white,line width=.35mm,line cap=round] (3.4,9)--(8.6,3.4);
    \fill[DLADEYellow] (10,8) circle (1.1);
    \node[anchor=west,text=white,font=\DisplayFont\bfseries\fontsize{15}{15}\selectfont] at (15,5.4) {DLADE};
  \end{tikzpicture}%
}

\newcommand{\Kicker}[1]{%
  {\color{DLADEBlue}\bfseries\fontsize{8.1}{10}\selectfont\MakeUppercase{#1}}%
}
\newcommand{\YellowKicker}[1]{%
  {\color{DLADEYellow}\bfseries\fontsize{8.1}{10}\selectfont\MakeUppercase{#1}}%
}
\newcommand{\DisplayTitle}[1]{%
  {\DisplayFont\bfseries\color{DLADENavyDark}\fontsize{20}{22}\selectfont #1}%
}
\newcommand{\BodyText}{\color{DLADEInk}\fontsize{9.3}{13.35}\selectfont}
\newcommand{\SmallBody}{\color{DLADEInk}\fontsize{8.7}{12.25}\selectfont}

\newcommand{\Badge}[4]{%
  \begin{textblock*}{55.3mm}(#1,70mm)
    \begin{tikzpicture}[x=1mm,y=1mm]
      \path[fill=white,draw=DLADEPaleBlue,line width=.25mm,rounded corners=2mm] (0,0) rectangle (55.3,-21);
      \fill[DLADEYellow] (0,0) rectangle (2.2,-21);
      \node[anchor=north west,text=DLADENavy,font=\DisplayFont\bfseries\fontsize{21}{21}\selectfont] at (6,-5.3) {#2};
      \node[anchor=north west,text=DLADEBlue,font=\bfseries\fontsize{7.9}{9}\selectfont] at (6,-14.1) {\MakeUppercase{#3}};
    \end{tikzpicture}
  \end{textblock*}%
}

\newcommand{\TimelineCard}[3]{%
  \begin{textblock*}{56mm}(#1,146mm)
    \begin{tikzpicture}[x=1mm,y=1mm]
      \path[fill=DLADEPale,rounded corners=1.5mm] (0,0) rectangle (56,-18);
      \fill[DLADEYellow] (5.5,-9) circle (1.5);
      \node[anchor=north west,text=DLADEBlue,font=\bfseries\fontsize{7.1}{8}\selectfont] at (10,-4.1) {\MakeUppercase{#2}};
      \node[anchor=north west,text=DLADEInk,font=\bfseries\fontsize{9}{10}\selectfont] at (10,-9.8) {#3};
    \end{tikzpicture}
  \end{textblock*}%
}

\newcommand{\Footer}[1]{%
  \begin{tikzpicture}[remember picture,overlay]
    \draw[DLADELine,line width=.2mm]
      ([xshift=17mm,yshift=13.5mm]current page.south west)--
      ([xshift=-17mm,yshift=13.5mm]current page.south east);
  \end{tikzpicture}
  \begin{textblock*}{78mm}(17mm,286.5mm)
    {\color{DLADEMuted}\fontsize{7.7}{9}\selectfont Dalian Analysis and Differential Equations}
  \end{textblock*}
  \begin{textblock*}{54mm}(78mm,286.5mm)
    \centering{\color{DLADEMuted}\fontsize{7.7}{9}\selectfont dalianade.github.io}
  \end{textblock*}
  \begin{textblock*}{30mm}(163mm,286.5mm)
    \raggedleft{\color{DLADEMuted}\fontsize{7.7}{9}\selectfont #1 / 2}
  \end{textblock*}%
}

\begin{document}

% =====================================================================
% PAGE 1
% =====================================================================
\begin{tikzpicture}[remember picture,overlay]
  \fill[DLADENavyDark] (current page.north west) rectangle ([yshift=-66mm]current page.north east);
  \fill[DLADEBlue] (current page.north west) rectangle ([xshift=8mm,yshift=-66mm]current page.north west);
  \fill[DLADEYellow] (current page.north west) rectangle ([yshift=-4mm]current page.north east);
\end{tikzpicture}

\begin{textblock*}{72mm}(17mm,15mm)\DLADELogo\end{textblock*}
\begin{textblock*}{92mm}(101mm,11.5mm)
  \raggedleft
  {\color{DLADEHeaderMuted}\fontsize{7.7}{9}\selectfont SCHOOL OF MATHEMATICAL SCIENCES}\\[1.2mm]
  {\color{DLADEHeaderMuted}\bfseries\fontsize{8.2}{9}\selectfont DUT - DALIAN UNIVERSITY OF TECHNOLOGY}
\end{textblock*}

\begin{textblock*}{126mm}(17mm,31mm)
  \YellowKicker{Recruitment \RecruitmentYear}\\[4.2mm]
  {\DisplayFont\bfseries\color{white}\fontsize{25.5}{28.5}\selectfont
  Open PhD \& Postdoc Positions\\in Applied Mathematics}
\end{textblock*}
\begin{textblock*}{44mm}(149mm,51.5mm)
  \raggedleft{\color{DLADEHeaderMuted}\fontsize{8.6}{10}\selectfont DALIAN, CHINA}
\end{textblock*}

\Badge{17mm}{03}{PhD openings}{1}
\Badge{77.3mm}{04}{Postdoc openings}{2}
\Badge{137.6mm}{2027}{Start year}{3}

\begin{textblock*}{176mm}(17mm,97mm)
  \Kicker{An invitation to apply}\\[2.3mm]
  {\BodyText
  We welcome applications to \textbf{\PhDOpenings\ PhD positions} and
  \textbf{\PostdocOpenings\ postdoctoral positions} in applied mathematics at the School of
  Mathematical Sciences, Dalian University of Technology (DUT), for the funding period
  \textbf{\FundingPeriod}. Applications are accepted on a rolling basis until all positions are filled.

  \vspace{2.2mm}
  The positions are based in Dalian, China. You will work in the research group of
  \textbf{Prof. Xian Liao} or \textbf{Prof. Lei Zhao}, with research focused on
  \textit{Analysis, Differential Equations, or Dynamical Systems}.

  \vspace{2.2mm}
  We offer an international research environment with regular seminars and workshops, and there is
  research funding for international conferences and (long-term) research visits. No Chinese is
  required, and English is the working language.}
\end{textblock*}

\TimelineCard{17mm}{PhD enrollment}{\PhDStart}
\TimelineCard{77mm}{Postdoc start}{From \PostdocStart}
\TimelineCard{137mm}{Applications}{Rolling until filled}

\begin{textblock*}{176mm}(17mm,176mm)
  \Kicker{01 / PhD positions}\\[2mm]
  \DisplayTitle{Four years. Three openings.}\\[2.2mm]
  {\SmallBody PhD positions are for four years, research-focused with no teaching obligation.
  A competitive mathematical background is preferred. The following documents are required for application:}
\end{textblock*}

\begin{textblock*}{176mm}(17mm,204mm)
  \begin{tikzpicture}[x=1mm,y=1mm]
    \path[fill=DLADEPale,draw=DLADEPaleBlue,line width=.25mm,rounded corners=2mm] (0,0) rectangle (176,-40);
    \fill[DLADEBlue] (0,0) rectangle (2.1,-40);
  \end{tikzpicture}
\end{textblock*}
\begin{textblock*}{161mm}(24mm,209mm)
  {\SmallBody
  \begin{enumerate}[leftmargin=5.2mm,itemsep=.8mm,topsep=0mm,label=\textbf{\arabic*.}]
    \item Cover letter (research interests and preferred supervisor).
    \item CV (including contact details of two academic referees).
    \item List of publications (if any).
    \item MSc thesis (if already available; otherwise: a description of the MSc thesis project).
    \item University diplomas/certificates and transcripts of records (BSc/MSc, if available).
  \end{enumerate}}
\end{textblock*}

\Footer{1}
\null\newpage

% =====================================================================
% PAGE 2
% =====================================================================
\begin{tikzpicture}[remember picture,overlay]
  \fill[DLADENavyDark] (current page.north west) rectangle ([yshift=-34mm]current page.north east);
  \fill[DLADEYellow] (current page.north west) rectangle ([yshift=-3mm]current page.north east);
\end{tikzpicture}

\begin{textblock*}{72mm}(17mm,15mm)\DLADELogo\end{textblock*}
\begin{textblock*}{92mm}(101mm,11.5mm)
  \raggedleft
  {\color{DLADEHeaderMuted}\fontsize{7.7}{9}\selectfont OPEN PHD \& POSTDOC POSITIONS}\\[1.2mm]
  {\color{DLADEHeaderMuted}\bfseries\fontsize{8.2}{9}\selectfont APPLIED MATHEMATICS / DALIAN, CHINA}
\end{textblock*}

\begin{textblock*}{176mm}(17mm,45mm)
  \Kicker{02 / Postdoctoral positions}\\[2mm]
  \DisplayTitle{Two years. Four openings.}\\[2.2mm]
  {\BodyText Postdoctoral positions are for two years, research-focused with no teaching obligation,
  and we offer a competitive salary. Applicants should be \textbf{under 32 years old at the time of
  appointment} and have \textbf{1-2 publications in internationally recognized journals}
  (arXiv preprints do not count).}\\[3mm]
  {\color{DLADEBlue}\bfseries\fontsize{10.2}{12}\selectfont REQUIRED APPLICATION DOCUMENTS}
\end{textblock*}

\begin{textblock*}{176mm}(17mm,82mm)
  \begin{tikzpicture}[x=1mm,y=1mm]
    \path[fill=DLADEPale,draw=DLADEPaleBlue,line width=.25mm,rounded corners=2mm] (0,0) rectangle (176,-39);
    \fill[DLADEBlue] (0,0) rectangle (2.1,-39);
  \end{tikzpicture}
\end{textblock*}
\begin{textblock*}{161mm}(24mm,87mm)
  {\SmallBody
  \begin{enumerate}[leftmargin=5.2mm,itemsep=1mm,topsep=0mm,label=\textbf{\arabic*.}]
    \item Cover letter (research interests and preferred supervisor).
    \item CV (including contact details of two academic referees).
    \item List of publications.
    \item Research statement (2-3 pages).
    \item PhD certificate (if already available; otherwise: expected date of defense).
  \end{enumerate}}
\end{textblock*}

% Application panel - paper style matching the position sections above
\begin{textblock*}{176mm}(17mm,129mm)
  \begin{tikzpicture}[x=1mm,y=1mm]
    \path[fill=DLADEPale,draw=DLADEPaleBlue,line width=.25mm,rounded corners=2mm] (0,0) rectangle (176,-88);
    \fill[DLADEBlue] (0,0) rectangle (2.1,-88);
  \end{tikzpicture}
\end{textblock*}
\begin{textblock*}{156mm}(27mm,139mm)
  \Kicker{03 / Application procedure}\\[4mm]
  {\DisplayFont\bfseries\color{DLADENavyDark}\fontsize{20.5}{24}\selectfont
  Submit one complete application as a single PDF.}\\[4mm]
  {\color{DLADEInk}\fontsize{9}{13}\selectfont
  Email the single PDF to the group at
  {\color{DLADEBlue}\bfseries\ObfuscatedEmail}.}\\[4mm]
  {\color{DLADEMuted}\fontsize{8.8}{12.5}\selectfont
  \textbf{Deadline:} Open until filled (rolling review). There will be a first committee meeting
  evaluating the application materials on \textbf{\FirstReviewDate}; subsequent reviews will then be
  conducted every three months.}

  \vspace{6mm}\color{DLADELine}\rule{156mm}{.2mm}\\[5mm]
  \Kicker{More information}\\[3mm]
  {\color{DLADEBlue}\bfseries\fontsize{10}{12}\selectfont\href{\Website}{\Website}}\\[1.5mm]
  {\color{DLADEMuted}\fontsize{7.8}{9}\selectfont DaLian Analysis and Differential Equations}
\end{textblock*}

\begin{tikzpicture}[remember picture,overlay]
  \fill[DLADEBlue]
    ([xshift=17mm,yshift=-225mm]current page.north west) rectangle
    ([xshift=-17mm,yshift=-225.3mm]current page.north east);
\end{tikzpicture}
\begin{textblock*}{176mm}(17mm,231mm)
  \Kicker{At a glance}
\end{textblock*}
\begin{textblock*}{81mm}(17mm,239mm)
  {\SmallBody
  \textbf{Host groups}\\Research group of Prof. Xian Liao or Prof. Lei Zhao.\\[4mm]
  \textbf{Research areas}\\Analysis, Differential Equations, or Dynamical Systems.}
\end{textblock*}
\begin{textblock*}{81mm}(112mm,239mm)
  {\SmallBody
  \textbf{Working environment}\\English is the working language; no Chinese is required.\\[4mm]
  \textbf{Research support}\\Funding for international conferences and (long-term) research visits.}
\end{textblock*}
\begin{textblock*}{176mm}(17mm,273mm)
  {\SmallBody\textbf{Institution}\\School of Mathematical Sciences, Dalian University of Technology,
  Linggong Road 2, 116024 Dalian, P.R. China.}
\end{textblock*}

\Footer{2}
\null
\end{document}
